---
title: "Lecture 1 | Welcome to Psych 101"
format: live-html
---


## Check-In, Agenda and Announcements

### Check-In.

{{< include ~/Dropbox/!WHY STATS/ystats/_extensions/r-wasm/live/_knitr.qmd >}}

```{webr}
for (x in 1:5) {
  print(x ** 2)
}
```

### Announcements

-   Section Swap : post on bCourses ASAP.
-   Next Week :
    -   Attend Discussion Section
    -   Complete Lab 1 (will start in lecture!)
    -   Read Chapter 2
    -   Complete Quiz 2
-   Waitlisted Students : Thanks for your patience! Nothing I can do :(
-   Join the Class Discord

### Agenda

-   2:10 - 2:30 \| Check-In & Announcements
-   2:30 - 3:00 \| RECAP : Science as Prediction

## R Practice : Defining Variables

### Thinking about Programming (Free Association Activity)

-   Close your eyes
-   Take a deep breath (inhale / exhale)
-   Visualize an image based on the word that you hear me say.
-   What do you observe?

## Recap : Science as Prediction

### Variables and Variation

### In R : Variables

+--------------------+---------------+
| Code               | Description   |
+====================+===============+
| ``` r              |               |
| test <- c(#,#,#,#) |               |
| ```                |               |
+--------------------+---------------+
|                    |               |
+--------------------+---------------+

#### Creating Numeric Variables

```{r}
counting <- c(1,2,3,4,5) # the numbers one through five
print(counting) # one way to "print" the variable
counting # another way to "print" the variable
hist(counting) # a way to graph the variable (a histogram)
```

#### Creating Non-Numeric Variables

```{r}
laundryhang <- c("shirt", "shirt", "leggings", "leggings", "shirt", 
             "shirt", "leggings", "pants", "sweater", "sweater") # defining a string variable
print(laundryhang)
laundryhang # another way to "print" the variable

laundryhang <- as.factor(laundryhang) # changing the format of the sting variable into a categorical factor
plot(laundryhang) # a way to graph the non-numeric variable
```

### Prediction & Error

### Epistemic Beliefs

## The Linear Model

### Definition

### Examples
